### 2015-01-20 src/analysis.Rnw
cleanup after amin

Suppose $M$ and $M_{strategy}$ denote the original set of mutants and  the reduced set of
mutants, respectively. 
% The strategy chooses $|M_{strategy}|$ mutants on its application. 
Test suite composed of test cases that 
are able to kill an $m$ where  $ m \in M_{strategy}$ is given by
$T_{strategy}$. The total number of \texttt{assert}s in $T_{strategy}$
is given by $asserts(T_{strategy})$. We find a minimal test suite that
is capable of killing all mutants under $M_{strategy}$ by a greedy algorithm
of iteratively choosing the test cases with the largest amount of kills
for remaining mutants, and is given by $min(T_{strategy})$. Similarly,
for baseline, we build set of randomly selected mutants $M_{random}$,
such that  $|M_{random}| = |M_{strategy}|$. Given any set of tests $T$,
the total number of mutants that can be killed by the test cases in $T$
is given by $k(T)$, and those mutants that are covered by the test cases
are given by $c(T)$.

@@

Positive value test utility denotes that the strategy requires more tests
and negative test utility denotes that the strategy needs less test cases.
Values close to zero basically denote that the strategy rouphly suggest the 
same number of tests. Note that the comparison here is betweeen the size of
tests and it does not imply any subset relationship between test suites.

@@

\textit{Strategy effectiveness} is computed by collecting all the test cases
that detected any of the mutants in the selected subset, and applying these
test cases to the complete set of mutants. The mutation score thus obtained
is then divided by the original number of detected mutants.
This is reported as difference from the corresponding baseline effectiveness,
given by 
\[\frac{|k(T_{strategy})| - |k(T_{random})|}{|k(M)|}\times100.0\]

>>>>

Let $M$ and $M_{strategy}$ denote the original set of mutants and the
reduced set of mutants respectively. Test suite composed of test cases
that are able to kill an $m$ where  $ m \in M_{strategy}$ is given by
$T_{strategy}$, and the total number of \texttt{assert}s in $T_{strategy}$
is given by $asserts(T_{strategy})$. We find a minimal test suite that is
capable of killing all mutants under $M_{strategy}$ by a greedy algorithm
of iteratively choosing the test cases with the largest amount of kills
for remaining mutants, and is given by $min(T_{strategy})$. Similarly, for
baseline, we build a set of randomly selected mutants $M_{random}$, such that
$|M_{random}| = |M_{strategy}|$. Given any set of tests $T$, the total number
of mutants that can be killed by the test cases in $T$ is given by $k(T)$,
and those mutants that are covered by the test cases are given by $c(T)$.

@@

Positive value test utility denotes that the strategy requires more tests
than random selection, and negative test utility denotes that the strategy
needs less test cases than random.  Values close to zero basically denote
that the strategy roughly suggest the same number of tests. Note that the
comparison here is between the size of tests and it does not imply any subset
relationship between test suites.

@@

\textit{Strategy effectiveness}~\footnote{Also called mutation score by Mresa
et al.~\cite{mresa1999efficiency}} is computed by collecting all the test
cases that detected any of the mutants in the selected subset, and applying
these test cases to the complete set of mutants. The mutation score thus
obtained is then divided by the original number of detected mutants.  This is
reported as difference from the corresponding baseline effectiveness, given by
\[\frac{|k(T_{strategy})| - |k(T_{random})|}{|k(M)|}\times100.0\]
